LSOA domestic Electricty and Gas maps

### 2021-09-17 LSOA domestic Elec and Gas.Rmd
Adding in basic plot for over 65s and electricity soncumsption fhe the whole UK for context
Adding OAC elect consumption and age graph

>>>>

```{r basic plot for over 65s and electricity consumption for whole UK }
ggplot(de_age, aes(x= 100 * prop_65m, 
                   y= mean_de2019))+ geom_point()
```
```{r over 65s and electricity with OAC codes}
oac_df <- readr::read_csv(paste0(dataFolder, "oac/lsoa-oac-data.csv"))
oac_df$la_name <- oac_df$`LA Name`
oac_df$LSOA11CD <- oac_df$`SOA Code`
solent_oac_df <- getSolent(oac_df)
df <- merge(Solent_2019, oac_df, by = "LSOA11CD")
ggplot(df, aes(x= 100 * prop_65m, 
                   y= mean_de2019, 
                   colour = `LA Name`)) + # use colour for each LA
  geom_point() +
  #theme(legend.position = "None") + # otherwise we get the colour legend at the side
  labs(x = "% aged > 65, 2011 Census",
       y = "Electricity Consumption (kWh per meter)") +
  facet_wrap(. ~ `Supergroup Name`) # draws a separate plot for each LA (in a different colour)
```
